---
title: "Replication Project mk2"
author: "Mason"
date: "1/16/2022"
output: 
  pdf_document:
    keep_tex: TRUE
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load dependences
library(ipumsr)
library(dplyr)
library(ggplot2)
library(crosswalkr)
library(table1)
library(expss) # apply_labels()
library(stargazer)
```

Import data
```{r}
ddi <- read_ipums_ddi("usa_00009.xml")

data <- read_ipums_micro(ddi)

set.seed(0001)

# Take 10% sample 
data = sample_frac(data, 0.10)
```

Cleaning data
```{r}
# Removing extremities 
data = data[data$INCWAGE != 0 &
             data$INCWAGE != 999998 &
             data$INCWAGE != 999999, ]
# Remove top and bottom 1% (outliers)
data = data %>% 
  group_by(YEAR) %>% 
  filter(INCWAGE < quantile(INCWAGE, 0.99) &
         INCWAGE > quantile(INCWAGE, 0.01)) %>%
  ungroup()
```

Set-up variables
```{r}
# Converting 'weeks worked' to 'weekly hours worked' (outputting the mean)
data = data %>% 
  mutate(
    wk_work_hrs = case_when(
      data$WKSWORK2 == 1 ~ 6.5,
      data$WKSWORK2 == 2 ~ 20,
      data$WKSWORK2 == 3 ~ 33,
      data$WKSWORK2 == 4 ~ 43.5,
      data$WKSWORK2 == 5 ~ 48.5,
      data$WKSWORK2 == 6 ~ 51
    )
  )

data = data %>% 
  mutate(
    log_work_hrs = ifelse(wk_work_hrs != 0, log(wk_work_hrs), 0)
  )

# Standardizing wages using CPI variable
data = data %>%
  mutate(
    avg_wk_earn = data$INCWAGE / data$wk_work_hrs * data$CPI99
  )

data = data %>%
  mutate(
    log_wk_earn = ifelse(avg_wk_earn != 0, log(avg_wk_earn), 0)
  )
```

Implement crosswalk
```{r}
occ_cw = read.csv("occ_crosswalk.csv")

# Delete N/A and unemployed
data = data[data$OCC1990 != 991 &
            data$OCC1990 != 999, ]

data$OCC1990 = encodefrom(data,
                          var = OCC1990,
                          occ_cw,
                          raw = occ1990,
                          clean = occ_2digit,
                          label = occ_2digit)

# Assigning jobs that pertains to the public sector as public variable
data$public = ifelse(data$OCC1990 == 1 |
                     data$OCC1990 == 10 |
                     data$OCC1990 == 11 |
                     data$OCC1990 == 42 |
                     data$OCC1990 == 82,
                     1, 0)
```

Set-up variables (continued)
```{r}
data$college_grad = ifelse(data$EDUC > 9, 1, 0)
data$some_college = ifelse(data$EDUC > 6 &
                           data$EDUC < 10, 1, 0)
data$hs_grad = ifelse(data$EDUC == 6, 1, 0)
data$less_than_hs = ifelse(data$EDUC < 6, 1, 0)

data = data %>%
  mutate(
    years_school = case_when(
      data$EDUC == 1 ~ 2.5,
      data$EDUC == 2 ~ 6.5,
      data$EDUC == 3 ~ 9,
      data$EDUC == 4 ~ 10,
      data$EDUC == 5 ~ 11,
      data$EDUC == 6 ~ 12,
      data$EDUC == 7 ~ 13,
      data$EDUC == 8 ~ 14,
      data$EDUC == 9 ~ 15,
      data$EDUC == 10 ~ 16,
      data$EDUC == 11 ~ 17
    )
  )

data = data %>%
  mutate(pot_work_exp = data$AGE - data$years_school - 6)

data = data %>% 
  mutate(sq_work_exp = pot_work_exp ^ 2)

data$married = ifelse(data$MARST < 3, 1, 0)

data$child_under5 = ifelse(data$NCHLT5 > 0, 1, 0)

data$foreign_born = ifelse(data$BPL > 119, 1, 0)

data$ne_region = ifelse(data$REGION < 14, 1, 0)
data$mw_region = ifelse(data$REGION > 13 & data$REGION < 24, 1, 0)
data$s_region = ifelse(data$REGION > 23 & data$REGION < 35, 1, 0)
data$w_region = ifelse(data$REGION > 34 & data$REGION < 44, 1, 0)

data$metro_area = ifelse(data$METRO > 1, 1, 0)
```

Create labels for the variables
```{r}
data = apply_labels(data,
                     avg_wk_earn = "Weekly wage",
                     log_wk_earn = "Weekly wage (logged)",
                     wk_work_hrs = "Weekly working hours",
                     log_work_hrs = "Weekly working hours (logged)",
                     public = "Public sector (=1)",
                     college_grad = "College graduate (=1)",
                     some_college = "Some college (=1)",
                     hs_grad = "High school graduate (=1)",
                     less_than_hs = "Less than high school (=1)",
                     pot_work_exp = "Potential work experience",
                     sq_work_exp = "Potential work experience sq.",
                     married = "Married (=1)",
                     NCHILD = "Number of children",
                     child_under5 = "Child under age 5 (=1)",
                     foreign_born = "Foreign born (=1)",
                     ne_region = "Northeast region (=1)",
                     mw_region = "Midwest region (=1)",
                     s_region = "South region (=1)",
                     w_region = "West region (=1)",
                     metro_area = "Lives in metropolitan area (=1)")
```

Split data 
```{r}
data2 = data[which(data$RACE == 1 |
                    data$RACE == 4 |
                    data$RACE == 5 |
                    data$RACE == 6), ]

data = data[which(data$RACE == 1 |
                   data$RACE == 2), ]
```

Create factors 
```{r}
data$RACE =
  factor(data$RACE,
         levels = c(1, 2),
         labels = c("White", "Black"))

data$YEAR =
  factor(data$YEAR,
         levels = c(1980, 1990, 2000, 2010),
         labels = c("1980", "1990", "2000", "2010"))
```

Split data
```{r}
data_male = data[which(data$SEX == 1), ]
data_female = data[which(data$SEX == 2), ]
```

Create table of coefficient means (for males)
```{r}
headers = c(split(data_male, 
                   f = list(data_male$RACE,
                            data_male$YEAR)))

labels = list(
  variables = list(
    avg_wk_earn = "Weekly wage",
    log_wk_earn = "Weekly wage (logged)",
    wk_work_hrs = "Weekly working hours",
    log_work_hrs = "Weekly working hours (logged)",
    public = "Public sector (=1)",
    college_grad = "College graduate (=1)",
    some_college = "Some college (=1)",
    hs_grad = "High school graduate (=1)",
    less_than_hs = "Less than high school (=1)",
    pot_work_exp = "Potential work experience",
    sq_work_exp = "Potential work experience sq.",
    married = "Married (=1)",
    NCHILD = "Number of children",
    child_under5 = "Child under age 5 (=1)",
    foreign_born = "Foreign born (=1)",
    ne_region = "Northeast region (=1)",
    mw_region = "Midwest region (=1)",
    s_region = "South region (=1)",
    w_region = "West region (=1)",
    metro_area = "Lives in metropolitan area (=1)"
  ),
  groups = list("1980", "1990", "2000", "2010")
)

my_render = function(x) {
  with(stats.default(x),
       sprintf("%0.2f", MEAN))
  }

table_male = table1(
  headers,
  labels,
  groupspan = c(2, 2, 2, 2),
  render.continuous = my_render,
  render.missing = NULL,
  rowlabelhead = "Variable"
  )
```

Index of Dissimilarity (for males)
```{r}
year = 1980
rows = 4
dissim_male = matrix(ncol = 2, nrow = rows)
colnames(dissim_male) = c("Year", "Index of Dissimilarity")

for (i in 1:rows){
  n = 82
  mymatrix = matrix(ncol = 2, nrow = n)
  colnames(mymatrix) = c("Occupation", "Difference")
  A = sum(data_male$RACE == "White" &
          data_male$YEAR == year)
  B = sum(data_male$RACE == "Black" &
          data_male$YEAR == year)
  
  for (j in 1:n){
    ai = sum(data_male$RACE == "White" & 
             data_male$YEAR == year &
             data_male$OCC1990 == j)
    bi = sum(data_male$RACE == "Black" & 
             data_male$YEAR == year &
             data_male$OCC1990 == j)
    difference = abs(ai/A - bi/B)
    mymatrix[j, ] = c(j, difference)
  }
  D = round(1/2 * sum(mymatrix[ , "Difference"]), 2)
  dissim_male[i, ] = c(year, D)
  year = year + 10
}
```

Create table of coefficient means (for females)
```{r}
headers = c(split(data_female,
                  f = list(data_female$RACE,
                           data_female$YEAR)))

table_female = table1(
  headers,
  labels,
  groupspan = c(2, 2, 2, 2),
  render.continous = my_render,
  render.missing = NULL,
  rowlabelhead = "Variable"
  )
```

Index of Dissimilarity (for females)
```{r}
year = 1980
rows = 4
dissim_female = matrix(ncol = 2, nrow = rows)
colnames(dissim_female) = c("Year", "Index of Dissimilarity")

for (i in 1:rows){
  n = 82
  mymatrix = matrix(ncol = 2, nrow = n)
  colnames(mymatrix) = c("Occupation", "Difference")
  A = sum(data_female$RACE == "White" &
          data_female$YEAR == year)
  B = sum(data_female$RACE == "Black" &
          data_female$YEAR == year)
  
  for (j in 1:n){
    ai = sum(data_female$RACE == "White" & 
             data_female$YEAR == year &
             data_female$OCC1990 == j)
    bi = sum(data_female$RACE == "Black" & 
             data_female$YEAR == year &
             data_female$OCC1990 == j)
    difference = abs(ai/A - bi/B)
    mymatrix[j, ] = c(j, difference)
  }
  D = round(1/2 * sum(mymatrix[ , "Difference"]), 2)
  dissim_female[i, ] = c(year, D)
  year = year + 10
}
```

Create Figure 1
```{r}
# How to color the lines by race?
data$SEX = factor(data$SEX,
                  levels = c(1, 2),
                  labels = c("Male",
                             "Female"))

fig_data = aggregate(data$avg_wk_earn ~ data$YEAR + data$RACE + data$SEX,
                     data, 
                     mean)

colnames(fig_data) = c("YEAR", "RACE", "SEX", "avg_wk_earn")

fig_data$YEAR = as.numeric(as.character(fig_data$YEAR))
fig_data$RACE = as.character(fig_data$RACE)
fig_data$SEX = as.character(fig_data$SEX)

fig_data$RACE_SEX = paste(fig_data$RACE, fig_data$SEX)

fig_plot = ggplot(
  fig_data,
  aes(x = YEAR,
      y = avg_wk_earn,
      shape = RACE_SEX,
      colour = RACE_SEX)) +
  geom_point(size = 2) + 
  geom_line(size = 0.5) +
  labs(x = "",
       y = "",
       title = "Average Weekly Earnings (in Constant USD) by Race and Gender from 1980 to 2010",
       subtitle = "White & Black") +
  ylim(300, 1000) +
  theme_bw() + 
  theme(aspect.ratio = 0.5,
        plot.title = element_text(size = 11),
        axis.text.x = element_text(face = "bold", colour = "black"),
        axis.text.y = element_text(face = "bold", colour = "black"),
        legend.title = element_blank(),
        legend.position = "bottom",
        legend.direction = "horizontal",
        legend.key.size = unit(0.5, "cm"),
        legend.text = element_text(size = 8),
        legend.background = element_rect(size = 0.4,
                                         linetype = "solid",
                                         colour = "black",
                                         fill = "white")) +
  guides(shape = guide_legend(ncol = 2))
```

Calculate regression coefficients (for males)
```{r}
# How to create loop for linear regression
m_ols = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data_male %>% filter(data_male$YEAR == "1980" & data_male$RACE == "White")) 

m_ols2 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data_male %>% filter(data_male$YEAR == "1980" & data_male$RACE == "Black")) 

m_ols3 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data_male %>% filter(data_male$YEAR == "1990" & data_male$RACE == "White")) 

m_ols4 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data_male %>% filter(data_male$YEAR == "1990" & data_male$RACE == "Black")) 

m_ols5 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data_male %>% filter(data_male$YEAR == "2000" & data_male$RACE == "White")) 

m_ols6 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data_male %>% filter(data_male$YEAR == "2000" & data_male$RACE == "Black")) 

m_ols7 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data_male %>% filter(data_male$YEAR == "2010" & data_male$RACE == "White")) 

m_ols8 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data_male %>% filter(data_male$YEAR == "2010" & data_male$RACE == "Black")) 

stargazer(m_ols, m_ols2, m_ols3, m_ols4, m_ols5, m_ols6, m_ols7, m_ols8,
          type = "text", column.sep.width = "1pt", omit.stat = c("f", "ser"),
          report = "vc",
          font.size = "footnotesize", 
          digits = 3,
          no.space = TRUE,
          column.labels = c("1980 W", "1980 B", "1990 W", "1990 B", 
                            "2000 W", "2000 B", "2010 W", "2010 B"))
```

Calculate regression coefficients (for females)
```{r}
f_ols = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data_female %>% filter(data_female$YEAR == "1980" & data_female$RACE == "White")) 

f_ols2 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data_female %>% filter(data_female$YEAR == "1980" & data_female$RACE == "Black")) 

f_ols3 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data_female %>% filter(data_female$YEAR == "1990" & data_female$RACE == "White")) 

f_ols4 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data_female %>% filter(data_female$YEAR == "1990" & data_female$RACE == "Black")) 

f_ols5 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data_female %>% filter(data_female$YEAR == "2000" & data_female$RACE == "White")) 

f_ols6 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data_female %>% filter(data_female$YEAR == "2000" & data_female$RACE == "Black")) 

f_ols7 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data_female %>% filter(data_female$YEAR == "2010" & data_female$RACE == "White")) 

f_ols8 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data_female %>% filter(data_female$YEAR == "2010" & data_female$RACE == "Black")) 

stargazer(f_ols, f_ols2, f_ols3, f_ols4, f_ols5, f_ols6, f_ols7, f_ols8,
          type = "text", column.sep.width = "1pt", omit.stat = c("f", "ser"),
          report = "vc",
          font.size = "footnotesize", 
          digits = 3,
          no.space = TRUE,
          column.labels = c("1980 W", "1980 B", "1990 W", "1990 B", 
                            "2000 W", "2000 B", "2010 W", "2010 B"))
```

Replication Part 2:
Pivoting analysis to White and Asian races using data2

Create factors
```{r}
data2$RACE = ifelse(data2$RACE > 1, 2, 1)

data2$RACE = factor(data2$RACE,
                    levels = c(1, 2),
                    labels = c("White", "Asian"))

data2$YEAR = factor(data2$YEAR,
                    levels = c(1980, 1990, 2000, 2010),
                    labels = c("1980", "1990", "2000", "2010"))
```

Split dataset
```{r}
data2_male = data2[which(data2$SEX == 1), ]
data2_female = data2[which(data2$SEX == 2), ]
```

Create table of coefficient means (for males)
```{r}
headers = c(split(data2_male,
                  f = list(data2_male$RACE,
                           data2_male$YEAR)))

table2_male = table1(
  headers,
  labels,
  groupspan = c(2, 2, 2, 2),
  render.continuous = my_render,
  render.missing = NULL,
  rowlabelhead = "Variable"
  )

colnames = c(
  "Variable",
  "White", "Asian",
  "White", "Asian",
  "White", "Asian",
  "White", "Asian"
  )
```

Index of Dissimilarity (for males)
```{r}
year = 1980
rows = 4

dissim2_male = matrix(ncol = 2,
                      nrow = rows)

colnames(dissim2_male) = c("Year", "Index of Dissimilarity")

for (i in 1:rows){
  n = 82
  mymatrix = matrix(ncol = 2,
                    nrow = n)
  colnames(mymatrix) = c("Occupation", "Difference")
  A = sum(data2_male$RACE == "White" &
          data2_male$YEAR == year)
  B = sum(data2_male$RACE == "Asian" & 
          data2_male$YEAR == year)
  
  for (j in 1:n){
    ai = sum(data2_male$RACE == "White" & 
             data2_male$YEAR == year &
             data2_male$OCC1990 == j)
    bi = sum(data2_male$RACE == "Asian" & 
             data2_male$YEAR == year &
             data2_male$OCC1990 == j)
    difference = abs(ai/A - bi/B)
    mymatrix[j, ] = c(j, difference)
  }
  D = round(1/2 * sum(mymatrix[ , "Difference"]), 2)
  dissim2_male[i, ] = c(year, D)
  year = year + 10
}
```

Create the table of coefficient means (for females)
```{r}
headers = c(split(data2_female,
                  f = list(data2_female$RACE,
                           data2_female$YEAR)))

table2_female = table1(
  headers,
  labels,
  groupspan = c(2, 2, 2, 2),
  render.continous = my_render,
  render.missing = NULL,
  rowlabelhead = "Variable"
  )
```

Index of Dissimilarity (for females)
```{r}
year = 1980
rows = 4

dissim2_female = matrix(ncol = 2,
                        nrow = rows)

colnames(dissim2_female) = c("Year", "Index of Dissimilarity")

for (i in 1:rows){
  n = 82
  mymatrix = matrix(ncol = 2,
                    nrow = n)
  colnames(mymatrix) = c("Occupation", "Difference")
  A = sum(data2_female$RACE == "White" &
          data2_female$YEAR == year)
  B = sum(data2_female$RACE == "Asian" & 
          data2_female$YEAR == year)
  
  for (j in 1:n){
    ai = sum(data2_female$RACE == "White" & 
             data2_female$YEAR == year &
             data2_female$OCC1990 == j)
    bi = sum(data2_female$RACE == "Asian" & 
             data2_female$YEAR == year &
             data2_female$OCC1990 == j)
    difference = abs(ai/A - bi/B)
    mymatrix[j, ] = c(j, difference)
  }
  D = round(1/2 * sum(mymatrix[ , "Difference"]), 2)
  dissim2_female[i, ] = c(year, D)
  year = year + 10
}
```

Figure 2
```{r}
data2$SEX = factor(data2$SEX,
                   levels = c(1, 2),
                   labels = c("Male", "Female"))

fig2_data = aggregate(data2$avg_wk_earn ~ data2$YEAR + data2$RACE + data2$SEX,
                      data2,
                      mean)

colnames(fig2_data) = c("YEAR", "RACE", "SEX", "avg_wk_earn")

fig2_data$YEAR = as.numeric(as.character(fig2_data$YEAR))
fig2_data$RACE = as.character(fig2_data$RACE)
fig2_data$SEX = as.character(fig2_data$SEX)

fig2_data$RACE_SEX = paste(fig2_data$RACE, fig2_data$SEX)

fig2_plot = ggplot(fig2_data,
                   aes(x = YEAR,
                       y = avg_wk_earn,
                       shape = RACE_SEX,
                       colour = RACE_SEX)) +
  geom_point(size = 2) + 
  geom_line(size = 0.5) + 
  labs(x = "",
       y = "",
       title = "Average Weekly Earnings (in Constant USD) by Race and Gender From 1980 to 2010",
       subtitle = "White & Asian") +
  ylim(300, 1000) +
  theme_bw() + 
  theme(aspect.ratio = 0.5,
        plot.title = element_text(size = 11),
        axis.text.x = element_text(face = "bold", colour = "black"),
        axis.text.y = element_text(face = "bold", colour = "black"),
        legend.title=element_blank(),
        legend.position = "bottom", 
        legend.direction = "horizontal",
        legend.key.size = unit(0.5, "cm"), 
        legend.text = element_text(size = 8), # font size of legends
        legend.background = element_rect(size=0.4,
                                         linetype="solid", 
                                         colour ="black",
                                         fill="white")) +
  guides(shape = guide_legend(ncol=2))
 
```

Calculate regression coefficients (for males)
```{r}
m_ols = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data2_male %>% filter(data2_male$YEAR == "1980" & data2_male$RACE == "White")) 

m_ols2 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data2_male %>% filter(data2_male$YEAR == "1980" & data2_male$RACE == "Asian")) 

m_ols3 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data2_male %>% filter(data2_male$YEAR == "1990" & data2_male$RACE == "White")) 

m_ols4 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data2_male %>% filter(data2_male$YEAR == "1990" & data2_male$RACE == "Asian")) 

m_ols5 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data2_male %>% filter(data2_male$YEAR == "2000" & data2_male$RACE == "White")) 

m_ols6 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data2_male %>% filter(data2_male$YEAR == "2000" & data2_male$RACE == "Asian")) 

m_ols7 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data2_male %>% filter(data2_male$YEAR == "2010" & data2_male$RACE == "White")) 

m_ols8 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data2_male %>% filter(data2_male$YEAR == "2010" & data2_male$RACE == "Asian")) 

stargazer(m_ols, m_ols2, m_ols3, m_ols4, m_ols5, m_ols6, m_ols7, m_ols8,
          type = "text", column.sep.width = "1pt", omit.stat = c("f", "ser"),
          report = "vc",
          font.size = "footnotesize", 
          digits = 3,
          no.space = TRUE,
          column.labels = c("1980 W", "1980 A", "1990 W", "1990 A", 
                            "2000 W", "2000 A", "2010 W", "2010 A"))
```

Calculate regression coefficients (for females)
```{r}
f_ols = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data2_female %>% filter(data2_female$YEAR == "1980" & data2_female$RACE == "White")) 

f_ols2 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data2_female %>% filter(data2_female$YEAR == "1980" & data2_female$RACE == "Asian")) 

f_ols3 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data2_female %>% filter(data2_female$YEAR == "1990" & data2_female$RACE == "White")) 

f_ols4 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data2_female %>% filter(data2_female$YEAR == "1990" & data2_female$RACE == "Asian")) 

f_ols5 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data2_female %>% filter(data2_female$YEAR == "2000" & data2_female$RACE == "White")) 

f_ols6 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data2_female %>% filter(data2_female$YEAR == "2000" & data2_female$RACE == "Asian")) 

f_ols7 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data2_female %>% filter(data2_female$YEAR == "2010" & data2_female$RACE == "White")) 

f_ols8 = lm(log_wk_earn ~ pot_work_exp + sq_work_exp + less_than_hs + hs_grad + some_college + NCHILD + child_under5 + married + foreign_born + log_work_hrs + metro_area + public + mw_region + s_region + w_region, data = data2_female %>% filter(data2_female$YEAR == "2010" & data2_female$RACE == "Asian")) 

stargazer(f_ols, f_ols2, f_ols3, f_ols4, f_ols5, f_ols6, f_ols7, f_ols8,
          type = "text", column.sep.width = "1pt", omit.stat = c("f", "ser"),
          report = "vc",
          font.size = "footnotesize", 
          digits = 3,
          no.space = TRUE,
          column.labels = c("1980 W", "1980 A", "1990 W", "1990 A", 
                            "2000 W", "2000 A", "2010 W", "2010 A"))
```

Compare figures
```{r}
gridExtra::grid.arrange(fig_plot, fig2_plot, ncol = 2)
```